R Notebook

### 2021-08-12 Paper_Figure_code.Rmd
tweaking figures

p_GSE77797_six_BPmet_each <- ggarrange(G6_BPmet[[1]], G6_BPmet[[2]], G6_BPmet[[3]], G6_BPmet[[4]], G6_BPmet[[5]], ncol = 2, nrow = 3)

@@

p_GSE77797_six_DHS_each <- ggarrange(G6_DHS[[1]], G6_DHS[[2]], G6_DHS[[3]], G6_DHS[[4]], G6_DHS[[5]], ncol = 2, nrow = 3)

figure_GSE77797_six_DHS_together <- ggarrange(p_GSE77797_six_DHS_all, p_GSE77797_six_DHS_each, ncol = 2, nrow = 1, labels = "c", font.label = list(size = 20, color = "black"), widths = c(1, 2))

@@

figure_GSE77797_six_BPmet_MethylCIBERSORT_DHS_together <- ggarrange(figure_GSE77797_six_BPmet_together, figure_GSE77797_six_MethylCIBERSORT_WB_together, figure_GSE77797_six_DHS_together, ncol = 1, nrow = 3)

@@

melt_GSE107011_BPRNA_EpiDISH[[4]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = NULL) +
  scale_y_continuous(name = NULL, limits = c(0, 0.5)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 18, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.475, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.405, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.0345, y = 0.335, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)

@@

p_GSE107011_BPRNA_EpiDISH_each <- ggarrange(melt_GSE107011_BPRNA_EpiDISH[[1]], melt_GSE107011_BPRNA_EpiDISH[[2]], melt_GSE107011_BPRNA_EpiDISH[[3]], melt_GSE107011_BPRNA_EpiDISH[[4]], melt_GSE107011_BPRNA_EpiDISH[[5]], melt_GSE107011_BPRNA_EpiDISH[[6]], ncol = 2, nrow = 3)

@@

Figure_4Sa <- ggarrange(p_benchmarker_CCLE_TIL10[[1]], p_benchmarker_CCLE_TIL10[[2]], p_benchmarker_CCLE_TIL10[[3]], p_benchmarker_CCLE_TIL10[[4]], p_benchmarker_CCLE_TIL10[[5]], p_benchmarker_CCLE_TIL10[[6]], p_benchmarker_CCLE_TIL10[[7]], p_benchmarker_CCLE_TIL10[[8]], p_benchmarker_CCLE_TIL10[[9]], p_benchmarker_CCLE_TIL10[[10]], p_benchmarker_CCLE_TIL10[[11]], ncol = 3, nrow = 4, labels = "a", font.label = list(size = 18, color = "black"))

@@

Figure_S4b <- ggarrange(bench_BPRNACan[[1]], bench_BPRNACan[[2]], bench_BPRNACan[[3]], bench_BPRNACan[[4]], bench_BPRNACan[[5]], bench_BPRNACan[[6]], bench_BPRNACan[[7]], bench_BPRNACan[[8]], bench_BPRNACan[[9]], ncol = 3, nrow = 3, labels = "b", font.label = list(size = 18, color = "black"))

>>>>

p_GSE77797_six_BPmet_each <- ggarrange(G6_BPmet[[1]], G6_BPmet[[2]], G6_BPmet[[3]], G6_BPmet[[4]], G6_BPmet[[5]], ncol = 2, nrow = 3, align = "hv")

@@

p_GSE77797_six_DHS_each <- ggarrange(G6_DHS[[1]], G6_DHS[[2]], G6_DHS[[3]], G6_DHS[[4]], G6_DHS[[5]], ncol = 2, nrow = 3, align = "hv")

figure_GSE77797_six_DHS_together <- ggarrange(p_GSE77797_six_DHS_all, p_GSE77797_six_DHS_each, ncol = 2, nrow = 1, labels = "c", font.label = list(size = 20, color = "black"), widths = c(1, 2), align = "hv")

@@

figure_GSE77797_six_BPmet_MethylCIBERSORT_DHS_together <- ggarrange(figure_GSE77797_six_BPmet_together, figure_GSE77797_six_MethylCIBERSORT_WB_together, figure_GSE77797_six_DHS_together, ncol = 1, nrow = 3, align = "hv")

@@

melt_GSE107011_BPRNA_EpiDISH[[4]] <- ggplot(melt_GSE107011_BPRNA_EpiDISH_modify[[4]], aes(x = value, y = V)) +
  geom_point(colour = c("darkgoldenrod1"), size = 6) +
  theme_bw() +
  stat_smooth(method = lm, color = "black", fullrange = T) +
  facet_wrap(~variable) +
  scale_x_continuous(name = NULL, limits = NULL) +
  scale_y_continuous(name = NULL, limits = c(0, 0.50)) +
  theme(strip.text.x = element_text(size = 18, color = "black", face = "bold"), text = element_text(size = 20)) +
  font("xy.text", size = 18, color = "black") +
  stat_cor(method = "pearson", aes(label = paste(..r.label.., ..p.label.., sep = "\n")), label.x = 0, label.y = 0.475, size = 6) +
  stat_cor(method = "pearson", aes(label = paste(..p.label.., sep = "\n")), label.x = 0, label.y = 0.405, size = 6) +
  theme(axis.title.y = element_text(vjust = 1.5)) +
  theme(axis.title.x = element_text(vjust = -0.5)) +
  annotate("text", x = 0.0345, y = 0.335, label = as.character(as.expression(substitute(paste(RMSE, " = ", r), list(r = round(RMSE$rmse[4], 2))))), parse = TRUE, size = 6)

@@

p_GSE107011_BPRNA_EpiDISH_each <- ggarrange(melt_GSE107011_BPRNA_EpiDISH[[1]], melt_GSE107011_BPRNA_EpiDISH[[2]], melt_GSE107011_BPRNA_EpiDISH[[3]], melt_GSE107011_BPRNA_EpiDISH[[4]], melt_GSE107011_BPRNA_EpiDISH[[5]], melt_GSE107011_BPRNA_EpiDISH[[6]], ncol = 2, nrow = 3, align = "hv")

@@

Figure_4Sa <- ggarrange(p_benchmarker_CCLE_TIL10[[1]], p_benchmarker_CCLE_TIL10[[2]], p_benchmarker_CCLE_TIL10[[3]], p_benchmarker_CCLE_TIL10[[4]], p_benchmarker_CCLE_TIL10[[5]], p_benchmarker_CCLE_TIL10[[6]], p_benchmarker_CCLE_TIL10[[7]], p_benchmarker_CCLE_TIL10[[8]], p_benchmarker_CCLE_TIL10[[9]], p_benchmarker_CCLE_TIL10[[10]], p_benchmarker_CCLE_TIL10[[11]], ncol = 3, nrow = 4, labels = "a", font.label = list(size = 18, color = "black"), align = "hv")

@@

Figure_S4b <- ggarrange(bench_BPRNACan[[1]], bench_BPRNACan[[2]], bench_BPRNACan[[3]], bench_BPRNACan[[4]], bench_BPRNACan[[5]], bench_BPRNACan[[6]], bench_BPRNACan[[7]], bench_BPRNACan[[8]], bench_BPRNACan[[9]], ncol = 3, nrow = 3, labels = "b", font.label = list(size = 18, color = "black"), align = "hv")
